Fast and exact visibility on digitized shapes and application to feature-aware normal estimation

### 2025-03-28 DGMM2025/paper.tex
introduction and basic definitions

    Definition Zd
    Definition Cell complex
    Definition Star

@@

@@

    \begin{definition}
        Two points \( p \) and \( q \) on \( K \) are visible if and only if the segment \([p, q]\) is included in \(\text{Star}(K)\), i.e., \( [p, q] \subseteq \text{Star}(K)\).
    \end{definition}

>>>>

    Visibility is a fundamental concept in computational geometry and digital topology, with applications ranging from computer vision to geometric modeling.
    In this work, we explore visibility through the lens of chord tangency, introducing a novel approach that builds on discrete geometric structures.
    Our framework leverages the discrete setting of and cell complexes, providing a rigorous foundation for analyzing visibility properties in digital spaces.

    We recall essential definitions from previous works, particularly the notions of , cell complexes, and the star operator as formalized in~\cite{lachaud:2021-dgmm} and~\cite{lachaud:2022-jmiv}.
    The integer grid serves as our primary space of study, where geometric structures are discretized using cell complexes.
    A cell complex is a decomposition of space into elementary units—vertices, edges, faces, and higher-dimensional counterparts—forming a combinatorial representation of geometric objects.
    The star of a cell, as defined in these works, consists of all higher-dimensional cells that contain it, a crucial concept for analyzing local neighborhoods and connectivity.

    Building on these foundations, our study focuses on visibility as determined by the tangency of chords in discrete geometry.
    We define and analyze how visibility relationships emerge in this context and investigate their combinatorial and topological implications.
    This approach provides a new perspective on discrete visibility, offering potential applications in digital imaging, surface reconstruction, and computational topology.

    The remainder of this paper is structured as follows.
    In Section 2, we formalize the concept of chord tangency and its role in visibility analysis.
    Section 3 enters into the usage of integer intervals intersections to quickly scan the figure in order to recover this visibiltiy.
    Section 4 presents our main results, using this visibility to compute normals using the CNC estimator~\cite*{lachaud:2022-dcg}.
    Finally, Section 5 concludes with some other applications of integer intervals intersections in the field.

@@

    Let $\Z^d$ be the d-dimensional digital space, $d$ > 0.
    Let $\mathcal{C}^d$ be the (cubical) cell complex induced by the lattice $\Z^d$ : its 0-cells are the points of $\Z^d$, its 1-cells are the open unit segments joining two 0-cells at distance 1, its 2-cells are the open unit squares, etc., and its d-cells are the d-dimensional open unit hypercubes with vertices in $\Z^d$.
    We denote $\mathcal{C}^d_k$ the set of its k-cells.
    In the following, a cell will always designate an element of $\mathcal{C}^d$, and the term subcomplex always designates a subset of $\mathcal{C}^d$.

    A cell $\sigma$ is a face of another cell $\tau$ whenever $\sigma$ is a subset of the topological closure $\bar{\tau}$ of $\tau$, written $\sigma \preccurlyeq \tau$.
    Given any subcomplex K of $\mathcal{C}^d$, the star $Star(K)$ of K is $\{\tau \in \mathcal{C}^d, s.t.\ \exists\sigma \in K,\sigma \preccurlyeq \tau\}$

@@

    \begin{definition}
        Two points \( p \) and \( q \) on \( K \) are visible if and only if the segment \([p, q]\) is included in \(\text{Star}(K)\), i.e.,\ \( [p, q] \subseteq \text{Star}(K)\)
    \end{definition}
